---
title: "Introduction to simmer.shiny"
author: "Andrie de Vries"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to simmer.shiny}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The `simmer.shiny` package uses discrete event simulation to help answer the questions:

* How big should my Shiny server be to handle `n` number of users?
* For a given size of server, how many users can Shiny handle?
* How should I tune the runtime parameters in RStudio Connect for my app?

The robust answer to this question is to use `shinyloadtest`, but for planning purposes you may want to rapidly develop some hypotheses and intuition about the problem, prior to building and testing an app.


## The `simmer` package

The `simmer` package makes it easy to build discrete event simulations in R. The `simmer.shiny` package uses `simmer` under the hood for defining and running the simulation.

## Run the simulation


```{r, fig.show='hold'}
library(simmer.shiny)
simmer_shiny()
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
