The `shimmer` package uses discrete event simulation to help answer the questions:

  * How big should my Shiny server be to handle `n` number of users?
  * For a given size of server, how many users can Shiny handle?
  * How should I tune the runtime parameters in RStudio Connect for my app?

The robust answer to this question is to use `shinyloadtest`, but for planning purposes you may want to rapidly develop some hypotheses and intuition about the problem, prior to building and testing an app.


## Relationship between `shimmer` and the `simmer` package

The `simmer` package makes it easy to build discrete event simulations in R. The `shimmer` package uses `simmer` under the hood for defining and running the simulation.

## Setting up the simulation

The `shimmer()` function reads a configuration file using the `config::get()` function.  The package contains a default configuration file at:

```{r}
system.file("config.yml", package = "shimmer")
```

The contents of this file:

```{r, echo=FALSE, comment = ""}
f <- readLines(system.file("config.yml", package = "shimmer"))
cat(f, sep = "\n")
```

## Run the simulation


```{r}
library(magrittr)
library(shimmer)
```

By default, the simulation runs for an hour (3,600 seconds) of simulation time:

```{r}
env <- shimmer()
env
```


## Plots

You can generate several plots from the simulation:


* CPU usage
* Response histogram
* Rejected connections (because the system was too busy)


```{r}
env %>%
  plot_shimmer_cpu_usage()
```
```{r}
env %>%
  plot_shimmer_response_histogram()
```

```{r}
env %>%
  plot_shimmer_rejection_usage()
```

In addition, you can also get more detail of the underlying system behaviour:

* Connections
* Connections per process


```{r}
env %>%
  plot_shimmer_connection_usage()
```

```{r}
env %>%
  plot_shimmer_process_usage()
```


