The `simmer.shiny` package uses discrete event simulation to help answer the questions:

  * How big should my Shiny server be to handle `n` number of users?
  * For a given size of server, how many users can Shiny handle?
  * How should I tune the runtime parameters in RStudio Connect for my app?

  The robust answer to this question is to use `shinyloadtest`, but for planning purposes you may want to rapidly develop some hypotheses and intuition about the problem, prior to building and testing an app.


## The `simmer` package

The `simmer` package makes it easy to build discrete event simulations in R. The `simmer.shiny` package uses `simmer` under the hood for defining and running the simulation.

## Setting up the simulation

The `simmer.shiny` function reads a configuration file using the `config::get()` function.  The package contains a default configuration file at:

  ```{r}
system.file("config.yml", package = "simmer.shiny")
```

The contents of this file:

  ```{r, echo=FALSE, comment = ""}
f <- readLines(system.file("config.yml", package = "simmer.shiny"))
cat(f, sep = "\n")
```

## Run the simulation


```{r}
library(magrittr)
library(simmer.shiny)
```

By default, the simulation runs for an hour (3,600 seconds):

  ```{r}
env <- simmer_shiny()
env
```


## Plots

```{r}
env %>%
  plot_shiny_usage()
```

```{r}
env %>%
  plot_shiny_resources()
```

```{r}
env %>%
  plot_shiny_cpu_histogram()
```

